Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-09 paper.tex
X_train, y_train

The estimator interface defines a \texttt{fit} method. This method is
called with training data (e.g., supplied as two arrays
\texttt{X} and \texttt{y} in supervised learning estimators). Its task
is to run a learning algorithm and to determine model-
specific parameters from the training data and set these as attributes on the
estimator object. As a convention, the parameters learned by an estimator are
exposed as public attributes\footnote{Note that the learned parameters are
different from the hyper-parameters given to the constructor. To distinguish
between the two, learned parameters are all suffixed with a trailing underscore
(e.g., \texttt{clf.coef\_} in the case of linear models is the vector of
coefficients learned from the data).} on the trained object.

>>>>

The estimator interface defines a \texttt{fit} method. This method is called
with training data (e.g., supplied as two arrays \texttt{X\_train} and
\texttt{y\_train} in supervised learning estimators). Its task is to run a
learning algorithm and to determine model- specific parameters from the training
data and set these as attributes on the estimator object. As a convention, the
parameters learned by an estimator are exposed as public
attributes\footnote{Note that the learned parameters are different from the
hyper-parameters given to the constructor. To distinguish between the two,
learned parameters are all suffixed with a trailing underscore (e.g.,
\texttt{clf.coef\_} in the case of linear models is the vector of
coefficients learned from the data).} on the trained object.
